Simulation of Nano Particles in a Laser Trap

### 2017-03-03 doc/draft4.tex
final version of the thesis

The thermal accomodation factor quantifies the behaviour of the interaction between the gas particles and the nano particle. Although Eq.

@@

\newpage
\section{Conclusion and Further Remarks}
% what does this all tell us? do we need to study more of this? 
In this thesis I have modeled an optical tweezer experiment with methods from the field of computational physics. The experiment was broken down into
different sections, that have been modeled separately. With the use of molecular dynamics I simulated the behaviour of a nano particle in a laser trap
and investigated the effects of the laser power and temperature of the surrounding gas on the center of mass movement of the nano particle.\\
The results show, that the center of mass temperature (and thus its movement) does indeed depend on the energy of the laser, as well as on the
pressure and temperature of the surrounding gas.\\
The development of the center of mass temperature shows a curve that seems to have a convex form, whereas the internal temperature shows a more
concave behaviour. So while the internal temperature initially grows faster, it could be possible for the center of mass temperature to pass the
internal temperature.\\
There are several ways to explore this subject further. The first idea would be to decrease the pressure even more and investigate the case of very low
energies, since this is not easily feasible in an experimental setup. Another idea would be to increase the number of atoms in the nano particle to
see if the surface of the particle plays a role in the development of the temperatures. Furthermore, the interaction between the gas particles and the
nano particle in the trap could be varied to include an attractive part in the potential. Generally, these simulations could be expanded by running
them on faster computers to investigate larger systems and expand the ranges of the involved values like pressure, laser
energy, and internal temperature.

>>>>

The thermal accomodation factor is a measure of the energy transfer during the interaction between the gas particles and the nano particle. Although Eq.

@@

\newpage
\section{Conclusion}
% what does this all tell us? do we need to study more of this? 
In this thesis I have modeled an optical tweezer experiment with methods from the field of computational physics. The experiment was broken down into
different sections, that have been modeled separately. With the use of molecular dynamics I simulated the behaviour of a nano particle in a laser trap
and investigated the effects of the laser power and temperature of the surrounding gas on the center of mass movement of the nano particle.\\
The results show, that the center of mass temperature (and thus its movement) does indeed depend on the energy of the laser, as well as on the
pressure and temperature of the surrounding gas.\\
The development of the center of mass temperature shows a curve that seems to have a convex form, whereas the internal temperature shows a more
concave behaviour. So while the internal temperature initially grows faster, it could be possible for the center of mass temperature to pass the
internal temperature.\\
There are several ways to explore this subject further. The first idea would be to decrease the pressure even more and investigate the case of very low
energies, since this is not easily feasible in an experimental setup. Another idea would be to increase the number of atoms in the nano particle to
see if the surface of the particle plays a role in the development of the temperatures. Furthermore, the interaction between the gas particles and the
nano particle in the trap could be varied to include an attractive part in the potential
to vary the thermal accomodation coefficient. Generally, these simulations could be expanded by running
them on faster computers to investigate larger systems and expand the ranges of the involved values like pressure, laser
energy, and internal temperature.
